### 2016-01-17 paper.tex
Add table of sensors

@@

Uncertainty was considered from a combination of systematic
and random errors. The random error was inferred from the sample standard
deviation and the systematic from the sensor calibrations or datasheets.
Combining both sources of error, along with their propagation into quantities
derived from multiple measurements, followed the procedures outlined in
Coleman and Steele (2009) \cite{ColemanSteele}, described below.

>>>>

\begin{table}[ht]
    \centering
    \begin{tabular}{c|c|c|c}
        Measured quantity & Device type & Mfg. \& model & Nominal accuracy \\
        \hline 
        Carriage position & Linear encoder & Renishaw LM15 & 10 $\mu$m/pulse \cite{RenishawLM15}\\
        Turbine angle & Servo encoder output & Kollmorgen AKD & 10$^5$ pulse/rev \cite{KollmorgenAKD}\\
        Turbine torque & Rotary transducer & Interface T8-200 & $\pm$0.5 Nm \cite{InterfaceT8}\\ 
        Turbine torque (2) & Load cell (\& arm) & Sentran ZB3-200 & $\pm$0.2 Nm \cite{SentranZB}\\
        Drag force, left & Load cell & Sentran ZB3-500 & $\pm$0.6 N \cite{SentranZB}\\
        Drag force, right & Load cell & Sentran ZB3-500 & $\pm$0.6 N \cite{SentranZB}\\
        Fluid velocity & ADV & Nortek Vectrino+ & $\pm$0.5\% $\pm$1 mm/s \cite{NortekVectrino}\\
    \end{tabular}
    \caption{Details of the sensors used in the experiment. Note that ``(2)''
        denotes a secondary redundant measurement. ``Turbine torque (2)'' nominal
        accuracy was estimated by combining load cell accuracy and arm machining
        tolerances ($\pm 1 \times 10^{-4}$ m) as root-sum-square.}
    \label{tab:sensors}
\end{table}

@@

Uncertainty was considered from a combination of systematic and random errors.
The random error was inferred from the sample standard deviation and the
systematic error from the sensor calibrations or datasheets. Combining both
sources of error, along with their propagation into quantities derived from
multiple measurements, followed the procedures outlined in Coleman and Steele
(2009) \cite{ColemanSteele}, described below.
